Community Embeddings for Friend Suggestions\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-10-11 conference_101719.tex
add comma

\begin{abstract}
    Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
    Recommender systems are used in a wide range of business applications and are essential for online e-business models to survive and strive in the contemporary market. Using graph embeddings for recommendation tasks, have the possibility of improving upon recommender systems, because of data compression, their feature vector format, and sub-quadratic time complexity.
    Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions. ComE BGMM+VI is an alteration of the community embeddings algorithm ComE. ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
    Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
\end{abstract}

>>>>

\begin{abstract}
    Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
    Recommender systems are used in a wide range of business applications and are essential for online, e-business models to survive and strive in the contemporary market. Using graph embeddings for recommendation tasks, have the possibility of improving upon recommender systems, because of data compression, their feature vector format, and sub-quadratic time complexity.
    Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions. ComE BGMM+VI is an alteration of the community embeddings algorithm ComE. ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
    Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
\end{abstract}
